\papertitle

### 2014-03-20 final-report/paper.tex
Move some content

For example, when querying how many workers are working on a certain fragment at a given time to produce the visualization described in Section~\ref{sec:fragments}, we used a query to select only events in the root operators (the operators that have no parent in the same fragment) for each fragment and a custom map function that carries state. The state is an integer that is incremented when the operator is called on a worker and decremented when the operator returns.

@@

We highly suggest that developers use the second approach when porting \system to a new DDBMS.

@@

The Myria web front-end server is written in Python and runs on Google App Engine\footnote{\url{https://developers.google.com/appengine/}}. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that were made possible using D3.

\system's front-end gets data from the Myria server using \system's back-end as JSON and CSV files. JSON objects are used to describe the physical queryplan. CSV files contain logs on query execution at the fragment and operator level as well as data exchange between workers at different stages of the query execution.

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Figure~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. Execution skew is visible as humps.
We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/utilization_chart}
  \caption{The utilization chart. }
  \label{fig:utilization_chart}
\end{figure}

@@

\subsubsection{Overview over all fragments}
\label{sec:fragments}

@@

This paper introduced \system, a visualization tool carefully tailored to help
database developers or users to quickly identify common distributed databases
performance bottlenecks, like tail latencies, data skew, etc. Our tool has been
successfully integrated with the Myria distributed database system, and has already
been used to identify several bugs, like poor physical query plan optimization,
tail latencies, poor data partitioning, which led us to believe the
visualization techniques we used are appropriate to help the user quickly
navigate to/find the cause of the performance problem. \system could be easily
plugged-in with another distributed database system, the only requirement being
a specific log data format.

>>>>

For example, when querying how many workers are working on a certain fragment at a given time to produce the visualization described in Section~\ref{sec:fragment}, we used a query to select only events in the root operators (the operators that have no parent in the same fragment) for each fragment and a custom map function that carries state. The state is an integer that is incremented when the operator is called on a worker and decremented when the operator returns.

@@

@@

The Myria web front-end server is written in Python and runs on Google App Engine\footnote{\url{https://developers.google.com/appengine/}}. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web.

\system's front-end gets data from the Myria server as JSON and CSV files. JSON is used to describe the physical queryplan. CSV files contain logs on query execution at the fragment and operator level as well as data exchange between workers at different stages of the query execution.

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Figure~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. Execution skew is visible as humps.
We implemented \emph{focus+context}\cite{furnas1986generalized} in form of
a small brush (at the top of the figure) that allows the user to zoom-in and further
analyze the problematic area without loosing the context of the whole execution.

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/utilization_chart}
  \caption{The utilization chart.}
  \label{fig:utilization_chart}
\end{figure}

@@

\subsubsection{Overview over all fragments}
\label{sec:overview}

@@

This paper introduced \system, a visualization tool carefully tailored to help
database developers or users to quickly identify common distributed databases
performance bottlenecks, like tail latencies, data skew, etc. Our tool has been
successfully integrated with the Myria distributed database system, and has already
been used to identify several bugs, like poor physical query plan optimization,
tail latencies, poor data partitioning, which led us to believe the
visualization techniques we used are appropriate to help the user quickly
navigate to/find the cause of the performance problem. \system could be easily
plugged-in with another distributed database system, the only requirement being
a specific log data format. We explained how we collect logs in Myria and recommend
our approach to developers that are porting \system to a new DDBMS.
